Simple models of deliberated preference

### 2018-01-27 simple.tex
Started using alternative notation with phi

$\ar$ is 
\begin{itemize}
	\item $\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$
	\item $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$
\end{itemize}

>>>>

We also define $\Phi = \alltopic × \set{\text{possible}, \text{sure}}$, and $\forall \phi = (\prop, \text{possible}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadstopst \prop$ and $\forall \phi = (\prop, \text{sure}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadstosst \prop$. We define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$. It follows that $¬¬\phi = \phi$. We write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$.
\footnote{From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \nileadstost ¬\phi$.}

$\ar$ is $\phi\text{-dec} ⇔ \forall \ar': (\ar', \ar) \ileadstost \prop$. We also say that $\ar$ is $\propsuredec$ or $\proppossdec$ when $\phi=(\prop, \text{sure})$ or $\phi=(\prop, \text{possible}$.
\footnote{$\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
